\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-14 Articles/IROS/root.tex
.
fixed, removed duplicated hadamard equation

The operating environment is modelled by discrete voxels. As the robots environment can dynamically change, we propose a method that looks at the surrounding space of the robot and calculates these direction away from all the surrounding obstacles in real time. We only look in a predefined area / perimeter arround the robot.

@@

By employing the Hadamard (element-wise) product (eq.~\ref{eq:hadamard}) between the cutout segment of the obstacle grid \(A_d\) and the corresponding 3D convolutional kernel \(K_d\) for direction \(d\), we derive the resultant matrix \(C_d\), which can be expressed as:

@@

\begin{equation}
	S = \sum_{i,j,k} (W \odot A)_{ijk} = \sum_{i}\sum_{j}\sum_{k} w_{\Delta i \Delta j \Delta k} ~  a_{\Delta i \Delta j \Delta k}
\end{equation}

Subsequently, the avoidance velocity in the Cartesian coordinate system is obtained (eq.~\ref{eq:summation}) by summing all the values in the resulting matrix $C_d$, which can be represented as:

\begin{equation}
	\dot{x}_{poi} = \sum_{i}\sum_{j}\sum_{k} c_{dijk} 
	\label{eq:summation}
\end{equation}

\alert{remove the above equation and add a vector of calculated velocities equation instead}

\comment{}{TODO: add the indexes for x,y,z directions}

@@

\comment{}{PLOT: kernel 2D images}
\comment{}{EQUATION: kernel generation / values equations}

>>>>

The robots environment is modelled by discrete voxels. As the robots environment can dynamically change, we propose a method that looks at the surrounding space of the robot and calculates these direction away from all the surrounding obstacles in real time. We only look in a predefined area / perimeter arround the robot.

@@

By employing the Hadamard (element-wise) product (eq.~\ref{eq:hadamard}) between the cutout segment of the obstacle grid \(G_d\) and the corresponding 3D convolutional kernel \(W_d\) and than summoning all of the matrix values for each of the directions $d \in \{x, y, z\}$, we derive the resultant repulsive velocities vector \( \vec{v}_i = \left[ v_{x_i} v_{y_i} v_{z_i}\right] \).

@@

\begin{equation}
	v_d = \sum_{i,j,k} (G \odot W)_{ijk} = \sum_{i}\sum_{j}\sum_{k} g_{\Delta i \Delta j \Delta k} ~  w_{\Delta i \Delta j \Delta k}
\end{equation}

%\begin{equation}
%	\dot{x}_{poi} = \sum_{i}\sum_{j}\sum_{k} c_{dijk} 
%	\label{eq:summation}
%\end{equation}
%
%\alert{remove the above equation and add a vector of calculated velocities equation instead}
%
%\comment{}{TODO: add the indexes for x,y,z directions}

@@

\comment{}{PLOT: kernel 2D images}
